troubleshooting

### 2025-11-12 README.Rmd

```{r}

library(dplyr)
library(mspms)

@@

peaks_prepared_data

```

@@

prepared_pd_data
```
### DIA-NN

@@

```{r}
precursor_filepath = system.file(
  "extdata/diann_report.pr_matrix.tsv",
  package = "mspms"
)
colData_filepath = system.file(
  "extdata/diann_colData.csv",
  package = "mspms"
)

prepared_diann_data <- prepare_diann(precursor_filepath,colData_filepath)

>>>>

```{r}
library(dplyr)
library(mspms)

@@

peaks_prepared_data
```

@@

prepared_pd_data
```
### Sage

Analysis of a lfq.tsv file exported from [sage](https://github.com/lazear/sage) is supported. We found this software a little harder to use than other solutions (No-GUI), however it is completly open-source, free, and by far the fastest!

```{r}
sage_lfq_filepath <- system.file(
  "extdata/sage_lfq.tsv",
  package = "mspms"
)

colData_filepath <- system.file("extdata/colData.csv",
  package = "mspms"
)

prepare_sage(sage_lfq_filepath, colData_filepath)
```

### DIA-NN

@@

```{r}
precursor_filepath <- system.file(
  "extdata/diann_report.pr_matrix.tsv",
  package = "mspms"
)
colData_filepath <- system.file(
  "extdata/diann_colData.csv",
  package = "mspms"
)

prepared_diann_data <- prepare_diann(precursor_filepath, colData_filepath)
